Stock enhancement undermines community stability

### 2022-02-08 rmd/manuscript.Rmd
edit: manuscript

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$. To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$), respectively. The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress]. In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003]. The fitness disadvantage of hatchery fish may add to negative density dependence to influence community stability.

@@

We should prioritize habitat conservation with a broader scope of ecosystem management. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.

>>>>

where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on species $i$, $K_i$ the carrying capacity, $R_t$ the number of released individuals for the enhancement of species 1, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that follow a normal distribution $Normal(0,\sigma_{\epsilon}^2)$. To capture variation in species traits, intrinsic growth rates of unenhanced species and interspecific competition coefficients were drawn randomly from a uniform ($r_{i,i \ne 1} \sim Unif(0,2)$) and an exponential distribution ($\alpha_{ij,i \ne j} \sim Exp(1/\bar{\alpha})$). The parameter $\phi_i$ controls the relative fitness of captive-bred individuals as follows:

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress]. In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003]. The fitness disadvantage may add to negative density dependence to influence community stability.

@@

We should prioritize habitat conservation with a broader scope of ecosystem management. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is a key to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
